Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-30 Article.tex
Article + biblio update

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation.
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.

>>>>

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation.
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{javidikia2023grain, dourandish2022microstructure, shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication, khan2021interactions}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{mha2022generalized} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
